Notes on generating initial models for mapping into {\tt MAESTRO}

### 2010-09-03 docs/initial_models/initial_models.tex
fix
add fine-coarse interpolation

Next we integrate up from the coarse-fine interface to the fine-cell center:
\begin{equation}
\frac{p_r^l - p_{r-\myhalf}^l}{\Delta r^l/2} = 
  \frac{\rho_r^l + \rho_{r-\myhalf}^l}{2} \,
  \frac{g_r^l + g_{r-\myhalf}^l}{2}
\end{equation}
We can rewrite this as an expression for the pressure at the fine-cell center:
\begin{equation}
p_r^l = p_{r-\myhalf}^l + \frac{\Delta r^l g}{8}
  \left(\rho_r^l + \rho_{r-\myhalf}^l\right)
  \left(g_r^l + g_{r-\myhalf}^l\right).
  \label{eq:itof}
\end{equation}
Combining equations \ref{eq:ctoi} and \ref{eq:itof} gives
\begin{eqnarray}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} &+& 
     \frac{\Delta r^{l-1}}{8} \left(\rho_{r-\myhalf}^l + \rho_{\sfrac{r}{2}-1}^{l-1}\right)
                                \left(   g_{r-\myhalf}^l +    g_{\sfrac{r}{2}-1}^{l-1}\right) \nonumber \\
 &+& \frac{\Delta r^l}{8} \left(\rho_r^l + \rho_{r-\myhalf}^l\right)
                            \left(   g_r^l +    g_{r-\myhalf}^l\right).
\end{eqnarray}
We can simplify using
\begin{equation}
\Delta r^{l-1} = 2\Delta r^l,
\end{equation}
and by interpolating the cell-centered densities to the coarse-fine interface as:
\begin{equation}
\rho_{r-\myhalf}^l = \frac{2}{3}\rho_r^l + \frac{1}{3}\rho_{\sfrac{r}{2}-1}^{l-1}.
\end{equation}
Because we carry both the cell- and edge-centered gravitational accelerations, we
do not need to interpolate $g$ to the interface.
Simplifying, we have
\begin{eqnarray}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} &+& 
   \frac{\Delta r^l}{4}\left(\frac{2}{3}\rho_r^l + 
                             \frac{1}{3}\rho_{\sfrac{r}{2}-1}^{l-1} + 
                             \rho_{\sfrac{r}{2}-1}^{l-1}\right) 
                       \left(   g_{r-\myhalf}^l +    g_{\sfrac{r}{2}-1}^{l-1}\right) \nonumber \\
  &+& \frac{\Delta r^l g}{8}\left(\rho_r^l + 
                                  \frac{2}{3}\rho_r^l + 
                                  \frac{1}{3}\rho_{\sfrac{r}{2}-1}^{l-1}\right) 
                       \left(   g_r^l +    g_{r-\myhalf}^l\right) \enskip .
\end{eqnarray}
Finally, we note for constant $g$, this simplifies to:
\begin{equation}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} + 
  \frac{3\Delta r^l g}{4}\left(\rho_{\sfrac{r}{2}-1}^{l-1} + \rho_r^l\right).\label{Coarse-Fine Stencil}
\end{equation}
When we encounter a change from fine to coarse, analogously
\begin{equation}
p_{(r+1)/2}^{l-1} = p_{r}^l + \frac{3\Delta r^l g}{4}\left(\rho_{r}^l+\rho_{(r+1)/2}^{l-1}\right).\label{Fine-Coarse Stencil}
\end{equation}

>>>>

Next we integrate up from the coarse-fine interface to the fine-cell center:
\begin{equation}
\frac{p_r^l - p_{r-\myhalf}^l}{\Delta r^l/2} = 
  \frac{\rho_r^l + \rho_{r-\myhalf}^l}{2} \,
  \frac{g_r^l + g_{r-\myhalf}^l}{2}
\end{equation}
We can rewrite this as an expression for the pressure at the fine-cell center:
\begin{equation}
p_r^l = p_{r-\myhalf}^l + \frac{\Delta r^l g}{8}
  \left(\rho_r^l + \rho_{r-\myhalf}^l\right)
  \left(g_r^l + g_{r-\myhalf}^l\right).
  \label{eq:itof}
\end{equation}
Combining equations \ref{eq:ctoi} and \ref{eq:itof} gives
\begin{eqnarray}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} &+& 
     \frac{\Delta r^{l-1}}{8} \left(\rho_{r-\myhalf}^l + \rho_{\sfrac{r}{2}-1}^{l-1}\right)
                                \left(   g_{r-\myhalf}^l +    g_{\sfrac{r}{2}-1}^{l-1}\right) \nonumber \\
 &+& \frac{\Delta r^l}{8} \left(\rho_r^l + \rho_{r-\myhalf}^l\right)
                            \left(   g_r^l +    g_{r-\myhalf}^l\right).
\end{eqnarray}
We can simplify using
\begin{equation}
\Delta r^{l-1} = 2\Delta r^l,
\end{equation}
and by interpolating the cell-centered densities to the coarse-fine interface as:
\begin{equation}
\rho_{r-\myhalf}^l = \frac{2}{3}\rho_r^l + \frac{1}{3}\rho_{\sfrac{r}{2}-1}^{l-1}.
\end{equation}
Because we carry both the cell- and edge-centered gravitational accelerations, we
do not need to interpolate $g$ to the interface.
Simplifying, we have
\begin{eqnarray}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} &+& 
   \frac{\Delta r^l}{4}\left(\frac{2}{3}\rho_r^l + 
                             \frac{4}{3}\rho_{\sfrac{r}{2}-1}^{l-1} \right)
                       \left(   g_{r-\myhalf}^l +    g_{\sfrac{r}{2}-1}^{l-1}\right) \nonumber \\
  &+& \frac{\Delta r^l g}{8}\left(\frac{5}{3}\rho_r^l + 
                                  \frac{1}{3}\rho_{\sfrac{r}{2}-1}^{l-1}\right) 
                       \left(   g_r^l +    g_{r-\myhalf}^l\right) \enskip .
\end{eqnarray}
Finally, we note for constant $g$, this simplifies to:
\begin{equation}
p_r^l = p_{\sfrac{r}{2}-1}^{l-1} + 
  \frac{3\Delta r^l g}{4}\left(\rho_{\sfrac{r}{2}-1}^{l-1} + \rho_r^l\right).\label{Coarse-Fine Stencil}
\end{equation}

When integrating across a fine-coarse interface (see Figure~\ref{fig:ftoc}), the proceduce is similar.
\begin{figure}[t]
\centering
\includegraphics[width=2.5in,angle=90]{\figpath/ftoc}
\caption{\label{fig:ftoc} A fine-coarse interface in the 1-d base state}
\end{figure}
The expression for general gravity becomes:
\begin{eqnarray}
p_{(r+1)/2}^{l-1} = p_{r}^l &+&
   \frac{\Delta r^l}{4}\left(\frac{2}{3}\rho_r^l + 
                             \frac{4}{3}\rho_{(r+1)/2}^{l-1} \right)
                       \left(   g_{(r+1)/2 -\myhalf}^{l-1} +    g_{(r+1)/2}^{l-1}\right) \nonumber \\
  &+& \frac{\Delta r^l g}{8}\left(\frac{5}{3}\rho_r^l + 
                                  \frac{1}{3}\rho_{(r+1)/2}^{l-1}\right) 
                       \left(   g_r^l +    g_{(r+1)/2 -\myhalf}^{l-1} \right) \enskip .
\end{eqnarray}
and for spatially-constant gravity, it simplifies to:
\begin{equation}
p_{(r+1)/2}^{l-1} = p_{r}^l + \frac{3\Delta r^l g}{4}\left(\rho_{r}^l+\rho_{(r+1)/2}^{l-1}\right).\label{Fine-Coarse Stencil}
\end{equation}
